Experiences with Planning for Natural Language Generation

### 2009-05-27 trunk/Papers/ci-spark/experiments.tex

Again we ran the experiment with FF 2.3 and SGPLAN 5.2.2; this time,
we also ran the experiment with the Metric-FF implementation of FF
because FF 2.3 had a bug that caused it to switch to a slower search
heuristic for larger problem instances, and which was fixed in
Metric-FF. The results are shown in
Fig.~\ref{fig:xtag-graph}. \todo{blah blah talk about results a bit}
Unlike in the referring expressions experiment above, our own
Graphplan implementation was unusably slow here for serious problem
instances---for $k=1$ and $n=3$, this planner took over two minutes,
and it exceeded its memory limit of 16 GB for $n>3$. \todo{blah blah
  talk about what we learn about FF etc}

>>>>

Fig.~\ref{fig:xtag-graph} reports the runtimes we measured in this
experiment for FF. Because the computations in this experiment were
very memory-intensive, we recompiled FF 2.3 as a 64-bit binary. We
also ran the experiments with a 64-bit version of Metric-FF; although
our planning problem is purely sequential and not metric, Metric-FF
avoids a bug which caused FF 2.3 to switch to a best-first search
strategy beyond a certain point; the jump in runtime is clearly
visible in the figure. We did not run this experiment with SGPLAN
because we didn not have access to a 64-bit version of either SGPLAN
5.2.2 or SGPLAN 6; some initial experiences with the 32-bit version
indicate that SGPLAN switches to FF's best-first strategy even for
small problem instances, and thus would be slower than the versions of
FF we reported here. We also do not report runtimes for our Java
implementation of Graphplan, because it was unusuably slow for serious
problem instances: For $k=1$ and $n=3$, it already took over two
minutes, and it exceeded its memory limit of 16 GB for
$n>3$.

\todo{blah blah talk about what we learn about FF etc}
search strategy matters; EHC search works pretty well; but again,
preprocessing takes tons of time.
